### 2016-07-26 notions.tex
messing with privacy notion
privacy

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A(M,\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivInd{\setprim}{A}$}\\
$b \getsr \bits$\\
$z \getsr A^{\RepOracle,\TestOracle}$\\
if $z = b$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\RepOracle(S_0,S_1)$}\\
if $\mathrm{used}=\true$ then \\
\nudge Ret $\bot$\\
if $|S_0|\neq|S_1|$ then \\
\nudge Ret $\bot$\\
$\mathrm{used}=\true$\\
$(M,\aux) \getsr \Rep(S_b)$\\
Return $\aux$\\

\medskip
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\
}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion. (Still playing...) \textcolor{red}{on the right, should $S_0,S_1$ be sampled from $\distr{\calS}{}$ instead?  This would be in line with the other notions}} 
\label{fig:privacy}
\end{figure}

\heading{Relationships among notions.}
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.  In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are effectively leaked in~$\aux$, you can't reliably produce~$M$ given~$(S,\aux)$.}
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }

>>>>

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A(M,\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.5}{.475}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$z \getsr A^{\RepOracle,\TestOracle}$\\
if $z = b$ then Return 1\\
Return 0\\
}
%
{
%\oracle{$\RepOracle(S_0,S_1)$}\\
\oracle{$\RepOracle()$}\\
if $\mathrm{used}=\true$ then Ret $\bot$\\
%if $|S_0|\neq|S_1|$ then \\
%\nudge Ret $\bot$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$\mathrm{used}=\true$\\
$(M,\aux) \getsr \Rep(S_b)$\\
Return $(S_0,S_1,\aux)$\\

\medskip
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\
}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion. (Still playing...)} 
\label{fig:privacy}
\end{figure}

\subsection{Relationships Among Notions}
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.  In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are effectively leaked in~$\aux$, you can't reliably produce~$M$ given~$(S,\aux)$.}
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }
